---
title: "LakeMichTribBacteria"
author: "Jared J. Homola"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# LakeMichTribBacteria 


LakeMichTribBacteria is a research compendium that brings together the data and analyses associated with *Sanfilippo et al. In Review. Watershed-scale landuse is associated with seasonal and spatial variation in Lake Michigan basin stream bacterial communities, Journal of Great Lakes Research.* 

Analysis scripts are provided in analysis/ and human-readable data in extData/. 

Note: All analyses originally conducted and package built using R version 4.0.0 in Windows 10

### To get started using the package

```{r eval=FALSE}
options(repos=structure(c(CRAN="http://cran.r-project.org")))
install.packages("devtools")
library(devtools)
install_github("ScribnerLab/LakeMichTribBacteria")
```

### /analysis contents
1. dbRDA.R: Distance-based redundancy analysis
2. dbRDA_correlationplot_04102020.R: Variable correlation plot
3. NMDSplots_03042020.R: Non-metric multidimensional scaling 
4. heatmap.R: Code for generating community heatmap figure
  
  

#### /analysis/mothur
1. 16S_V4_Tiny_data_interactive_mothur_script_PDS_101019_TM_nodistseqscutoff_10162019_1112021.txt: Mothur script to process metabarcoding data. See https://mothur.org/ for more information
2. Bacterial_Mothur_cons_tax_and_shared_file_processing.R: Mothur post-processing script
  
  

### /extData contents
1. stability.trim.contigs.good.unique.good.filter.unique.pick.precluster.pick.opti_mcc.0.03.cons.taxonomy: The taxonomy file from Mothur (input for file 2. of /analysis/mothur)
2. stability.trim.contigs.good.unique.good.filter.unique.pick.precluster.pick.opti_mcc.0.03.subsample.shared: Subsample file (input for file 2. of /analysis/mothur)
3. Bacterial_OTU_Matrix.txt
4. 2019Bacteria_RiverCoordinates_LkMich.csv: Site coordinates
5. RiverNames_01112021.xlsx: Site names
6. bacteria_state.xlsx: Key for site state based on naming scheme
7. bacteria_time.xlsx: Key for sampling time based on naming scheme
8. bacteria_rivers_reduced_landscape_vars_raw_&_transformed.xlsx: Landscape variables



#### Contact
Kim T. Scribner  <br>
scribne3@msu.edu  <br> 

Jared J. Homola  <br>
jaredhomola20@gmail.com <br> 
www.jaredhomola.com  

#### Copyright (c) 2021 ScribnerLab

Permission is hereby granted, free of charge, to any person obtaining a copy
of this software and associated documentation files (the "Software"), to deal
in the Software without restriction, including without limitation the rights
to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
copies of the Software, and to permit persons to whom the Software is
furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all
copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
SOFTWARE.
